Global code motion of congruent instructions

### 2017-04-17 paper.tex
split gcm

@@

% Explain the overall algorithm, explain how anticipability is computed on demand
\begin{verbatim}
int doCodeHoisting()
  Analyses available: Dominator Tree, DFS Numbering, Memory SSA,

  Compute GVN of each expression in the function
  Compute DJ-graph of function and compute mergeset based on that

  For each value number VN with 2 or more instructions:
    sort the instructions according to DFSIn numbers
    if first two I1, I2 are hoistable:
      if they are downward-safe at hoist-point:
        if they are profitable to be hoisted at hoist-point:
          proceed to check hoistability of subsequent instruction with same VN
        else
          proceed to check if I2 and I3 (if available) is hoistable

@@

  return number_of_hoisted_candidates

If any of candidates were hoisted then repeat hoisting
\end{verbatim}

Once no more candidates are hoistable proceed to sinking

\begin{verbatim}
Analyses available: Dominator Tree, DFS Numbering, Memory SSA, Mergeset
Compute GVN of each expression in the function

For each value number VN with 2 or more instructions:
  if there are two instructions with same immediate successor as post-dominator
    if both are only used in the same PHI-node of the successor
      if both have dependencies that are available or can be made available at the sink point
         mark VN as sinkable

@@

Code size also remained almost the same as a result of code-motion as shown in
Table~\cite{tab:code-size}.  The code size listed here is the text size (from
linux size command) of the final executables for each benchmark.  Some bencmarks
like 473.astar increased in code size by almost 2\%. This is because once the
code-size of a function decreases it becomes cheaper to inline. As we can see in
Table-\cite{tab:stats}, four more functions got inlined in 473.astar. Except for
447.dealII, 450.soplex, 482.sphinx3 and 483.xalancbmk all other benchmarks got
more functions inlined.

>>>>

\begin{verbatim}
void doGCM()
  Analyses available: Dominator Tree, DFS Numbering, Memory SSA,
  Compute DJ-graph of function and compute mergeset based on that
  do
    Compute GVN of each expression in the function
    int N = doCodeHoisting()
  while (N > 0) // If any of candidates were hoisted then repeat hoisting
  doCodeSinking()
\end{verbatim}

@@

% Explain the overall algorithm, explain how anticipability is computed on demand
\begin{verbatim}
int doCodeHoisting()
  For each value number VN with 2 or more instructions:
    sort the instructions according to DFSIn numbers
    if first two I1, I2 are hoistable:
      if they are downward-safe at hoist-point:
        if they are profitable to be hoisted at hoist-point:
          proceed to check hoistability of subsequent instruction with same VN
        else
          proceed to check if I2 and I3 (if available) is hoistable

@@

  return number_of_hoisted_candidates
\end{verbatim}

After no more candidates are hoistable, sinking is performed. Sinking is only
performed once becase currently there are very few sinkable candidates
(Table~\ref{tab:code-motion-metric}) as SimplifyCFG of LLVM (which runs before
GCM) has a (suboptimal) code-sinking which sinks several instructions already.

\begin{verbatim}
void doCodeSinking()
  For each value number VN with 2 or more instructions:
    if there are two instructions with same immediate successor as post-dominator
      if both are only used in the same PHI-node of the successor
        if both have dependencies that are available or can be made available at the sink point
           mark VN as sinkable

@@

Code size also remained almost the same as a result of code-motion as shown in
Table~\cite{tab:code-size}.  The code size listed here is the text size (from
linux size command) of the final executables for each benchmark.  Some bencmarks
like 473.astar increased in code size by almost 2\%. This is because once the
code-size of a function decreases it becomes cheaper to inline. As we can see in
Table-\ref{tab:stats}, four more functions got inlined in 473.astar. Except for
447.dealII, 450.soplex, 482.sphinx3 and 483.xalancbmk all other benchmarks got
more functions inlined.
